Using \LaTeX\ to submit manuscripts to peer reviewed journals.

### 2014-04-08 docs/thesis/chap-theoretical_background.tex
work on document: added conclussions, future work, general review.
work on title page
fixes to the thesis document

A further variation that takes into account structure in the form of a document containing different fields and each of them having its own length and importance (boost) can be formulated as follows, known as BM25F can be expressed as follows:

@@

\section{Latent Semantic Indexing}

\section{Latent Dirichlet Allocation}

>>>>

A further variation that takes into account structure in the form of a document containing different fields and each of them having its own length and importance (boost), known as BM25F can be expressed as follows:

@@
